\section{Conclusion}
\label{sec:conclusion}

We presented \emph{\mm}, a novel approach providing a model to implement unobtrusive functional additions to or modifications of an existing networked system without touching any proprietary components.
By classifying a networked system into the \emph{system}, i.e., components containing proprietary or other not changeable parts, and the \emph{environment}, i.e., components containing modifiable parts under control, 
behavioral changes are achieved by mechanism-enhancing yet unobtrusive \emph{interceptors},
i.e., a layer that is introduced between environment and system adding or updating mechanisms.
Such an interceptor can have many forms like an updated software library, a newly deployed edge device, or an enhanced cloud service.
Interceptors must be unobtrusive to avoid disrupting or even breaking applications but still provide added or modified mechanisms to the networked systems.

We illustrate this approach by applying the findings of the model in two case studies
that show its real-world applicability.
First, we unobtrusively replace a cloud infrastructure by an edge infrastructure in a wireless sensor network.
Second, we unobtrusively add a vertical handover mechanism between Wi-Fi and LTE to a mobile end device without disconnecting TCP sessions.
Our results indicate that \mm is a compelling approach to achieve improved service quality and provide previously unavailable functionality in an unobtrusive manner.

The contributions of this paper are:
\begin{itemize}
    \item We present \mm, a model that can be used by developers to design and implement unobtrusive mechanism interceptors.
    \item We present two examples, NAT and Wine, which serve as a basis for developing the \mm model.
    \item We present an application, \ttt, where our model is applied to replace a cloud infrastructure by an edge infrastructure to unobtrusively add previously unavailable functionality in a sensor network.
    \item We present an application, where our model is applied to add an unobtrusive vertical handover mechanism between Wi-Fi and LTE and thereby improve service quality of mobile devices.
\end{itemize}

The remainder of this paper is organized as follows.
Section~\ref{sec:releted_work} presents related work.
Section~\ref{sec:design} introduces two real-world examples and the derived model for \mm.
Section~\ref{sec:treetalker} presents the first case-study, \ttt and Section~\ref{sec:wg:impl} presents the second case-study, \wgh.
Section~\ref{sec:conclusion} concludes this paper and presents future work.
